SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-19 Chapters/sdm-autocorrelation.tex
SDM Autocorrelation vanishes when n -> infty.

>>>>

\begin{theorem}
Let $r$ be the access radius given that $f$ percent of the hard locations are activated. Then, $\lim_{n \rightarrow \infty} r/n = 1/2$.
\label{thm:sdm-access-radius}
\end{theorem}
\begin{proof}
Let $\text{ppf}$ be the inverse of the cdf of the standard normal distribution. Then,

\begin{align}
r &= \frac{d}{2} + \text{ppf}(f) \frac{\sqrt{d}}{2} \\
\frac{r}{d} = \frac{1}{2} + \text{pff}(f) \frac{1}{2 \sqrt{d}}
\end{align}

Thus, $d \rightarrow \infty \Rightarrow r/d \rightarrow 1/2$.
\end{proof}

\begin{theorem}
$\lim_{n \rightarrow \infty} P(x_i = y_i | d(x, y) \le r) = 1/2$
\label{thm:sdm-autocorrelation-convergence}
\end{theorem}
\begin{proof}

From \ref{thm:sdm-access-radius}, we know that $\lim_{n \rightarrow \infty} = d/2$.

For $k$ even, then:

$$
\sum_{k=0}^{r} \binom{n}{k} = \sum_{k=0}^{n/2} \binom{n}{k} = \frac{2^d}{2} = 2^{d-1}
$$

$$
\sum_{k=0}^{r} \binom{n-1}{k} = \sum_{k=0}^{n/2} \binom{n}{k} = \frac{2^{d-1}}{2} - \frac{1}{2} \binom{d-1}{d/2}
$$

\begin{align}
P(x_i = y_i | d(x, y) \le r) &= \frac{\sum_{k=0}^{r} \binom{n-1}{k}}{\sum_{k=0}^{r} \binom{n}{k}} \\
    &= \frac{2^{d-2} - \frac{1}{2} \binom{d-1}{d/2}}{2^{d-1}} \\
    &= \frac{2^{d-2}}{2^{d-1}} - \frac{1}{2^d} \binom{d-1}{d/2} \\
    &= \frac{1}{2} - \frac{1}{2^d} \binom{d-1}{d/2}
\end{align}

As $d \rightarrow \infty \Rightarrow \frac{1}{2^d} \binom{d-1}{d/2} \rightarrow 0$, the proof is done.

For $k$ odd, the proof is equivalent.

In Figure \ref{fig:sdm-10kbits-figure-7-3}, $n=10,000$ and we can notice that the autocorrelation has vanished as predicted by Theorem \ref{thm:sdm-autocorrelation-convergence}.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.75\textwidth]{./images02/sdm-10000bits-10000w-table-7-2.png}

  \caption{Given an address $x$ and a dimension $i$, how many hard locations with bitmatches in $i$ are activated by reading at $x$?  The histogram was obtained through numerical simulation. The red curve is the theoretical normal distribution found in Theorem \ref{T2}.}
  \label{fig:sdm-10kbits-figure-7-3}
\end{figure}
